Weather Data Integration and Assimilation System\\

### 2020-02-09 results/sec_2-work_load.tex
Workload is a single word
Cleanup TODOs

\dbc{Workload is a single word.}

do I need to talk about system setup with EKS?
add another section for performance tuning?
\dbc{Sifficient details need to be given.}

== Starts with how locations are created
As explained in the \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
While generating the timeseries for performance testing, it selected locations all over the world as a generic case to include all the locations without binding to a specific area.

These locations https://developers.google.com/public-data/docs/canonical/countries\_csv are static though out the testing, and data added to the wdias-performance-test.
During the performance test, it creates 1000 timeseries and keep adding data against those timeseries. For each location, it creates four timeseries with vary with module Id key attribute with four values. Thus combining all together, those creates 1000 timeseries. But test cases generate these values before starts the performance tests, and able to increase the timeseries as wanted.

@@

== Then using those, create timeseries metadata (how it assure 10% of Grid data)
In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomised} create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time. jmeter best practices lean\_mean}. Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \ref{se:test_plan}.
Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}. This occurs in the setup phase of the test cases. The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.

== Then how precipitation data for each time period created
The system is capable of storing any numeric value up to 3 decimal points. It does not make any different based on the parameter type whether it is the precipitation or the temperature. Thus during the performance testing, \acrshort{jmeter} uses real precipitation data from \acrshort{curw}. One month period of data for five weather stations have been using for prepare the test data. The script to cleanup and prepare the precipitation data is available as \emph{setup\_precipitation.sh} in wdias-performance.

@@

== Then how water level data for Grid time series created
Almost similar to how was the precipitation data proceed, the water level are prepared for Grid data. One exception with Grid data during this test cases was, the maximum time step is 30min, instead of 15min due to larger size of the data. But the \acrshort{wdias} is capable of supporting such request. The main purpose of the \acrshort{wdias} is to provide a extensible architecture framework, during the performance testing it is not much consider about scaling the Grid data handling as it using \acrshort{netCDF}, and it is another domain with an attraction up to some extend.

@@

== Talk about the test test up - JMeter
=== mentioned distributed setup test data collect issue and continue with one server coz it can support what is required
\subsection{Experimental Setup}
In order to create higher work load using the \acrshort{jmeter}, it has Distributed Testing feature. It uses the master slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances. But it has following limitation;
\say{Note: The same test plan runs by all the servers. JMeter does not distribute the load between servers, each runs the full test plan. So if you set 1000 Threads and have 6 JMeter server, you end up injecting 6000 Threads}. When test cases runs with \acrshort{jmeter} Distributed mode, the server node trigger same copy of test case on configured slave nodes parallel. At the end of the test cases, it gather results into the master node.

@@

== Talk about Stepping timer with concurrent thread group
When implementing load test cases with \acrshort{jmeter}, it uses threads to simulate the users. The root component of a test create is a thread group. There are different kind of thread groups are available such as Thread Group (Basic thread group), Arrivals Thread Group, Free Form Arrivals Thread Group, Stepping Thread Group, Concurrency Thread Group and Ultimate Thread Group etc.

TODO
\subsubsection{closed vs. open workload models} \cite{Haggett1998AnWales}
\label{subse:closed_vs_open_workload}
\begin{itemize}
    \item \emph{closed system model} a new request is only triggered by the completion of a previous request, following by a think time. System has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
    \item \emph{open system model} new requests arrival independently of completions, e.g.,according to a stochastic process or fixed trace. System has no negative feedback.
\end{itemize}
While implementing the test cases for \acrshort{wdias}, it uses Concurrency Thread Group with Throughput Shaping Timer because of it support the open workload approach.
Using other thread groups, it required to find exact number of threads and timer delays that produce desired number of requests per second (RPS) to server. Which is known as the \emph{closed workload}.
With using Throughput Shaping Timer, it only need to configure the \acrfull{rps}. When combine this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target RPS \cite{Haggett1998AnWales} TODO.

== Add screenshot of jmeter setup
The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The \ref{fi:wdias_performance_test} shows the overall figure of all the test cases.

@@

== talk about test plans can run
As per the usage description of test-dev, it has the features of enable a test case, disable a test case, and run the test case while enabled.
Another wrapper was implemented around the test-dev as \emph{test-plan.sh} which is also available with the code base \cite{Haggett1998AnWales} TODO.

@@

- e.g., diagram indicating the nodes and their connectivity (load generator, target, storage, etc.), Then briefly describe the diagram.

>>>>

As explained in the \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
While generating the timeseries for performance testing, it selected locations all over the world as a generic case to include all the locations without binding to a specific area.

These locations are taken from Google's Countries Public Dataset \cite{GoogleCountriesPublicDataset}, and consider static though out the testing, and data added to the wdias-performance-test.
During the performance test, it creates 1000 timeseries and keep adding data against those timeseries. For each location, it creates four timeseries with vary with module Id key attribute with four values. Thus combining all together, those creates 1000 timeseries. But test cases generate these values before starts the performance tests, and able to increase the timeseries as wanted.

@@

In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomised} create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time. jmeter best practices lean\_mean}. Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \ref{se:test_plan}.
Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}. This occurs in the setup phase of the test cases. The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.

The system is capable of storing any numeric value up to 3 decimal points. It does not make any different based on the parameter type whether it is the precipitation or the temperature. Thus during the performance testing, \acrshort{jmeter} uses real precipitation data from \acrshort{curw}. One month period of data for five weather stations have been using for prepare the test data. The script to cleanup and prepare the precipitation data is available as \emph{setup\_precipitation.sh} in wdias-performance.

@@

Almost similar to how was the precipitation data proceed, the water level are prepared for Grid data. One exception with Grid data during this test cases was, the maximum time step is 30min, instead of 15min due to larger size of the data. But the \acrshort{wdias} is capable of supporting such request. The main purpose of the \acrshort{wdias} is to provide a extensible architecture framework, during the performance testing it is not much consider about scaling the Grid data handling as it using \acrshort{netCDF}, and it is another domain with an attraction up to some extend.

@@

\subsection{Experimental Setup}
In order to create higher workload using the \acrshort{jmeter}, it has Distributed Testing feature. It uses the master slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances. But it has following limitation;
\say{Note: The same test plan runs by all the servers. JMeter does not distribute the load between servers, each runs the full test plan. So if you set 1000 Threads and have 6 JMeter server, you end up injecting 6000 Threads}. When test cases runs with \acrshort{jmeter} Distributed mode, the server node trigger same copy of test case on configured slave nodes parallel. At the end of the test cases, it gather results into the master node.

@@

When implementing load test cases with \acrshort{jmeter}, it uses threads to simulate the users. The root component of a test create is a thread group. There are different kind of thread groups are available such as Thread Group (Basic thread group), Arrivals Thread Group, Free Form Arrivals Thread Group, Stepping Thread Group, Concurrency Thread Group and Ultimate Thread Group etc.

\subsubsection{closed vs. open workload models} \cite{Haggett1998AnWales}
\label{subse:closed_vs_open_workload}
\begin{itemize}
    \item \emph{closed system model} a new request is only triggered by the completion of a previous request, following by a think time. System has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
    \item \emph{open system model} new requests arrival independently of completions, e.g.,according to a stochastic process or fixed trace. System has no negative feedback.
\end{itemize}
While implementing the test cases for \acrshort{wdias}, it uses Concurrency Thread Group with Throughput Shaping Timer because of it support the open workload approach.
Using other thread groups, it required to find exact number of threads and timer delays that produce desired number of requests per second (RPS) to server. Which is known as the \emph{closed workload}.
With using Throughput Shaping Timer, it only need to configure the \acrfull{rps}. When combine this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target RPS \cite{Haggett1998AnWales} TODO.

The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The \ref{fi:wdias_performance_test} shows the overall figure of all the test cases.

@@

As per the usage description of test-dev, it has the features of enable a test case, disable a test case, and run the test case while enabled.
Another wrapper was implemented around the test-dev as \emph{test-plan.sh} which is also available with the code base \cite{Haggett1998AnWales} TODO.

@@

\dbc{- e.g., diagram indicating the nodes and their connectivity (load generator, target, storage, etc.), Then briefly describe the diagram.}
